### 2019-04-12 Docs/Communications/ignored/XTerM2019/extendedAbstract.tex
abstract_ectqg

\cite{raimbault2018indirect}
\cite{raimbault2018calibration}

@@

\cite{reuillon2013openmole}

>>>>

The generic multi-scalar model is based on a coupling of several instances of local urban morphogenesis models, and more particularly the reaction-diffusion model studied by \cite{raimbault2018calibration}, through a macroscopic model of interaction between these areas in the spirit of \cite{raimbault2018indirect}. It is therefore able to (i) integrate long range interactions in systems of cities and (ii) simulate the local urban form.

We assume model ontologies similar to the original ones and operate the coupling through a potential dependency of parameters between scales. Let the index $\mu$ denote the macro scale and $M$ the meso scale. Then we assume the parameters of reaction-diffusion instances to depend on time and the macro-scale: $(\alpha,\beta,N_G/P_m)\left[t,\mu\right]$ and similarly for the parameters of the interaction model $(g_0,\vec{gamma},d_G)\left[t,M\right]$.
% TODO Note : here a clarification is needed : shouldnt the macro ontology be a bit modified to include short range and long range interactions ? then cannot be fully generic ?

We are interested in the following coupling specifications: weak coupling $\mu \rightarrow M$ (no upward causation, study of the consequence on local form of global dynamics), weak coupling $M \rightarrow \mu$ (no downward causation, aggregation of macro trajectories based on macro dynamics to e.g. study their performance compared to the model alone) and strong coupling $M \leftrightarrow \mu$ which can implemented in different ways, but which implies upward and downward causations. The comparison between these coupling is in itself an important knowledge.

@@

The model is implemented in scala for performance purposes and an easier integration into the model exploration software OpenMOLE \cite{reuillon2013openmole}.
